### 2017-11-07 submission/manuscript.Rmd
add fig legend 4 and 5 to manuscript

**Figure 4: **

**Figure 5: **

>>>>

**Figure 4: OTU Random Forest Model of Stool Across Studies.** A) Adenoma random forest model between the full community and CRC associated genera OTUs only. B) Carcinoma random forest model between the full community and CRC associated genera OTUs only. The dotted line represents an AUC of 0.5 and the lines represent the range in which the AUC for the 100 different 80/20 runs fell between.

**Figure 5: OTU Random Forest Model of Tissue Across Studies.** A) Adenoma random forest model between the full community and CRC associated genera OTUs only. B) Carcinoma random forest model between the full community and CRC associated genera OTUs only. The dotted line represents an AUC of 0.5 and the lines represent the range in which the AUC for the 100 different 80/20 runs fell between.

### 2017-11-07 submission/manuscript.tex
add fig legend 4 and 5 to manuscript

\textbf{Figure 4: }

\textbf{Figure 5: }

>>>>

\textbf{Figure 4: OTU Random Forest Model of Stool Across Studies.} A)
Adenoma random forest model between the full community and CRC
associated genera OTUs only. B) Carcinoma random forest model between
the full community and CRC associated genera OTUs only. The dotted line
represents an AUC of 0.5 and the lines represent the range in which the
AUC for the 100 different 80/20 runs fell between.

\textbf{Figure 5: OTU Random Forest Model of Tissue Across Studies.} A)
Adenoma random forest model between the full community and CRC
associated genera OTUs only. B) Carcinoma random forest model between
the full community and CRC associated genera OTUs only. The dotted line
represents an AUC of 0.5 and the lines represent the range in which the
AUC for the 100 different 80/20 runs fell between.
